PInSoRo: A Dataset for Deep-learning of Human-Robot Social Interactions

### 2017-06-21 paper.tex
Intro: cite Ogata's work

While the family of \emph{recurrent neural networks} have repeatedly made the
headlines over the last few years with impressive results, notably in image
classification, image labelling and automatic translation, they have been 
largely ignored in many other fields so far as they are perceived to require very
large datasets (hundreds of thousands to millions of observations) to actually
build up useful capabilities. Even though neural networks have demonstrated
compelling results in open-ended, under-defined tasks like image labelling, they
did not stand out as attractive approaches to problems involving high dimensions
with relatively small datasets available -- like human-robot social
interactions.

@@

In 2015, the Google DeepMind team demonstrated how a convolutional
recurrent neural network could learn to play the game Break-Out (amongst
48 other Atari games) by only \emph{looking} at the gaming console
screen~\cite{mnih2015human}. This result represents a major milestone: they show
that a relatively small sample size (about 500 games) is sufficient for an 
artificial agent to not only learn how to play (which requires an implicit model 
of time to adequately move the Break-Out paddle), but to also create gaming 
strategies that \emph{look like} they would necessitate planning (the system first
breaks bricks on one side to eventually get the ball to break-out and reach the area
\emph{above} the remaining bricks, therefore ensuring rapid progress in the
game). We argue that the complexity of mechanisms that such a neural network has been able
to quickly uncover and model should invite our
community to question its applicability to human-robot interactions (HRI) in general,
and sustained, natural child-robot interactions in particular.

However, the lack of a widespread HRI dataset suitable for the training of
neural networks is a critical obstacle to this initial exploration. We present
hereafter such a dataset, and detail our acquisition methodology.

@@

Kim \etal~\cite{kim2015pororobot} highlight that applying deep learning to
visual scene information in an HRI scenario was successful, but that
generating behaviours for the robot to be able to act in a dynamic and uncertain
environment remains a challenge.
\todo[inline]{cite Ogata's work}

>>>>

While the family of recurrent neural networks (RNN) have repeatedly made the
headlines over the last few years with impressive results, notably in image
classification, image labelling and automatic translation, they have been so far 
largely ignored by  many other fields as they are perceived to require very
large datasets (hundreds of thousands to millions of observations) to actually
build up useful capabilities. Even though neural networks have demonstrated
compelling results in open-ended, under-specified tasks like image labelling, they
did not stand out as attractive approaches to problems involving high dimensions
with relatively small datasets available -- like human-robot social
interactions.

@@

In 2015, the Google DeepMind team demonstrated how a convolutional
recurrent neural network could learn to play the game Break-Out (amongst
48 other Atari games) by only \emph{looking} at the gaming console
screen~\cite{mnih2015human}. This result represents a major milestone: they show
that a relatively small sample size (about 500 games) is sufficient for an 
artificial agent to not only learn how to play (which requires an implicit model 
of time to adequately move the Break-Out paddle), but to also create gaming 
strategies that \emph{look like} they would necessitate planning (the system first
breaks bricks on one side to eventually get the ball to break-out and reach the area
\emph{above} the remaining bricks, therefore ensuring rapid progress in the
game).

More recently, Ogata's team~\cite{yang2017repeatable} has demonstrated how an
adequately configured RNN is able to learn a complex robotic task (folding soft
objects like towels using a dual-arm mobile manipulator) from only \emph{35}
demonstrations, one demonstration being a $\approx$ 70 seconds-long teleoperated
sequence. The network inputs are the raw video stream from the head camera and the
12 DoF of the two arms and the total training dataset comprises of about 28000
steps of data.

We argue that the complexity of mechanisms that such neural networks have been
able to uncover and model should invite our community to question its
applicability to human-robot interactions in general, and sustained, natural
child-robot interactions in particular.

However, the current lack of an appropriate HRI dataset suitable for the training of
neural networks hinders this investigation. We present hereafter such a dataset,
and detail our acquisition methodology.

@@

Kim \etal~\cite{kim2015pororobot} highlight that applying deep learning to
visual scene information in an HRI scenario was successful, but that
generating behaviours for the robot to be able to act in a dynamic and uncertain
environment remains a challenge.
